On The Subspace Learning for Network Attack Detection

### 2019-06-14 docs/thesis/chapters/5_conclusion_future_work/conclusion.tex
after fix bold notation

\begin{itemize}
	\item Improvements for obtaining better false positive rates, as well as for make the proposed framework able to identify sparse probe attacks or subtle behaviors, such as exfiltration or covert communication, considering the evaluation of a flow-based analysis and novel data sets;
	\item Distributed or parallel processing can also be evaluated to analyze the scalability and processing capacity for monitoring high throughput network traffic;
	\item Evaluate the application of the proposed approach to different anomaly detection problems, considering cases that are aware to behavioral analysis;
	\item Enhance the m-RPCA approaches to estimate the contamination or not rely on previously defined contamination for anomaly detection;
\end{itemize}

>>>>

\begin{itemize}
	\item Improvements for obtaining better false positive rates, as well as to make the proposed framework able to identify sparse probe attacks or subtle behaviors, such as exfiltration or covert communication, considering the evaluation of a flow-based analysis and novel data sets;
	\item Distributed or parallel processing can also be evaluated to analyze the scalability and processing capacity for monitoring high throughput network traffic;
	\item Evaluate the application of the proposed approaches to different anomaly detection problems, considering cases that are aware to behavioral analysis;
	\item Enhance the m-RPCA approaches to estimate the contamination or to not rely on previously defined contamination for anomaly detection;
	\item The m-RPCA can also be extended to be online and to learn new subspace in a adaptive fashion, by means of new robust subspace learning from new observations or through robust subspace tracking.
\end{itemize}
